The SMT Competition 2015--2018

### 2019-02-01 2018/report/SMT-COMP.tex
Less inaccurate meta-data
Add Alt-Ergo reference

\jsatheading{1}{2004}{1-25}
\ShortHeadings{The SMT Competition 2015--2018}
{Weber et al.}
\firstpageno{1}

@@

\published{November 2018}{November 2018}{November 2018}

@@

\begin{table}
  \caption{Participants (2015--2018)}
  \label{table:participants}
  \centering
  \begin{tabular}{|l|p{11.5cm}|}
    \hline
    Solver & Submitters (Affiliations)\\
    \hline
    ABC~\cite{DBLP:conf/cav/BraytonM10} & Valeriy Balabanov
                        (Mentor Graphics)\\
    Alt-Ergo          & Albin Coquereau
                        (CNRS and University of Paris-Sud)\\
    AProVE~\cite{DBLP:conf/cade/GieslBEFFOPSSST14} & Carsten Fuhs
                        (University College London; Birkbeck, University of London)\\
    Boolector~\cite{DBLP:conf/cav/NiemetzPWB18} & Mathias Preiner
                        (Johannes Kepler University)\\
    COLIBRI~\cite{colibri} & Fran\c{c}ois Bobot
                        (French Alternative Energies and Atomic Energy Commission)\\
    Ctrl-Ergo         & Mohamed Iguernlala
                        (CNRS and University of Paris-Sud)\\
    CVC3~\cite{DBLP:conf/cav/BarrettT07} & Kshitij Bansal
                        (New York University)\\
    CVC4~\cite{DBLP:conf/cav/BarrettCDHJKRT11}  & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                        (New York University; Stanford University)\\
    MapleSTP          & Jimmy Liang
                        (University of Waterloo)\\
    MinkeyRink        & Trevor Hansen
                        (University of Melbourne)\\
    OpenSMT2~\cite{DBLP:conf/sat/HyvarinenMAS16} & Matteo Marescotti, Antti Hyv\"arinen
                        (University of Lugano)\\
    ProB~\cite{doi:10.1002/9781119002727.ch14} & Sebastian Krings
                        (University of D\"usseldorf)\\
    Q3B               & Martin Jon\'a\v{s}
                        (Masaryk University)\\
    raSAT~\cite{rasat} & Tung Vu Xuan
                        (Japan Advanced Institute of Science and Technology)\\
    Redlog~\cite{DBLP:journals/cca/Dolzmann097} & Haniel Barbosa
                        (Inria Nancy)\\
    SMT-RAT~\cite{DBLP:conf/sat/CorziliusKJSA15} & Florian Corzilius, Gereon Kremer
                        (RWTH Aachen University)\\
    SMTInterpol~\cite{DBLP:conf/spin/ChristHN12} & J\"urgen Christ
                        (University of Freiburg)\\
    SPASS-SATT         & Martin Bromberger
                        (Max Planck Institute for Informatics)\\
    STP~\cite{ganesh07} & Mate Soos, Trevor Hansen, Norbert Manthey
                        (National University of Singapore; University of Melbourne; Amazon Web Services)\\
    toysmt             & Masahiro Sakai
                        (Toshiba Corporation)\\
    Vampire~\cite{DBLP:conf/cav/KovacsV13} & Giles Reger
                        (University of Manchester)\\
    veriT~\cite{DBLP:conf/cade/BoutonODF09} & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
    XSat~\cite{DBLP:conf/cav/FuS16} & Martin Velez
                        (University of California, Davis)\\
    Yices2~\cite{Dutertre:cav2014} & Bruno Dutertre, Dejan Jovanovi\'c
                        (SRI International)\\
    Z3~\cite{DBLP:conf/tacas/MouraB08} & Christoph Wintersteiger, Aleksandar Zelji\'c
                        (Microsoft Research; Uppsala University)\\
    \hline
  \end{tabular}
\end{table}

>>>>

\jsatheading{?}{2018}{??-??}
\ShortHeadings{The SMT Competition 2015--2018}
{Weber et al.}
\firstpageno{1}

@@

\published{November 2018}{TBA}{TBA}

@@

\begin{table}
  \caption{Participants (2015--2018)}
  \label{table:participants}
  \centering
  \begin{tabular}{|l|p{11.5cm}|}
    \hline
    Solver & Submitters (Affiliations)\\
    \hline
    ABC~\cite{DBLP:conf/cav/BraytonM10} & Valeriy Balabanov
                        (Mentor Graphics)\\
    Alt-Ergo~\cite{conchon:hal-01960203} & Albin Coquereau
                        (CNRS and University of Paris-Sud)\\
    AProVE~\cite{DBLP:conf/cade/GieslBEFFOPSSST14} & Carsten Fuhs
                        (University College London; Birkbeck, University of London)\\
    Boolector~\cite{DBLP:conf/cav/NiemetzPWB18} & Mathias Preiner
                        (Johannes Kepler University, Stanford University)\\
    COLIBRI~\cite{colibri} & Fran\c{c}ois Bobot
                        (French Alternative Energies and Atomic Energy Commission)\\
    Ctrl-Ergo         & Mohamed Iguernlala
                        (CNRS and University of Paris-Sud)\\
    CVC3~\cite{DBLP:conf/cav/BarrettT07} & Kshitij Bansal
                        (New York University)\\
    CVC4~\cite{DBLP:conf/cav/BarrettCDHJKRT11}  & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                        (New York University; Stanford University)\\
    MapleSTP          & Jimmy Liang
                        (University of Waterloo)\\
    MinkeyRink        & Trevor Hansen
                        (University of Melbourne)\\
    OpenSMT2~\cite{DBLP:conf/sat/HyvarinenMAS16} & Matteo Marescotti, Antti Hyv\"arinen
                        (University of Lugano)\\
    ProB~\cite{doi:10.1002/9781119002727.ch14} & Sebastian Krings
                        (University of D\"usseldorf)\\
    Q3B               & Martin Jon\'a\v{s}
                        (Masaryk University)\\
    raSAT~\cite{rasat} & Tung Vu Xuan
                        (Japan Advanced Institute of Science and Technology)\\
    Redlog~\cite{DBLP:journals/cca/Dolzmann097} & Haniel Barbosa
                        (Inria Nancy)\\
    SMT-RAT~\cite{DBLP:conf/sat/CorziliusKJSA15} & Florian Corzilius, Gereon Kremer
                        (RWTH Aachen University)\\
    SMTInterpol~\cite{DBLP:conf/spin/ChristHN12} & J\"urgen Christ
                        (University of Freiburg)\\
    SPASS-SATT         & Martin Bromberger
                        (Max Planck Institute for Informatics)\\
    STP~\cite{ganesh07} & Mate Soos, Trevor Hansen, Norbert Manthey
                        (National University of Singapore; University of Melbourne; Amazon Web Services)\\
    toysmt             & Masahiro Sakai
                        (Toshiba Corporation)\\
    Vampire~\cite{DBLP:conf/cav/KovacsV13} & Giles Reger
                        (University of Manchester)\\
    veriT~\cite{DBLP:conf/cade/BoutonODF09} & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
    XSat~\cite{DBLP:conf/cav/FuS16} & Martin Velez
                        (University of California, Davis)\\
    Yices2~\cite{Dutertre:cav2014} & Bruno Dutertre, Dejan Jovanovi\'c
                        (SRI International)\\
    Z3~\cite{DBLP:conf/tacas/MouraB08} & Christoph Wintersteiger, Aleksandar Zelji\'c
                        (Microsoft Research; Uppsala University)\\
    \hline
  \end{tabular}
\end{table}
